---
title: "Boston 1999"
output:
  pdf_document: default
  html_notebook: default
---
In this document I will analyze the agglomeration of nonprofit industries in Boston and Dallas/Ft. Worth. I will remove all zipcodes with only 1 nonprofit as well as all industries with only one nonprofit and then look at the distribution of gammas.
```{r}
load("/home/samutavi/Documents/Coe College/Spellman 2018/RData/US1999.Rdata")
boston <- subset.data.frame(US1999, US1999$CITY == "BOSTON" & US1999$STATE == "MA")
#Subsetting further by industry and zipcodes, using only those that have more than 1 nonprofit.
boston2 <- subset.data.frame(boston, boston$zipnew == "2105" | boston$zipnew == "2206" | boston$zipnew == "2210")
boston3 <- subset.data.frame()

dallas <- subset.data.frame(US1999, US1999$CITY == "DALLAS" | US1999$CITY == "FORT WORTH" & US1999$STATE == "TX")
```
Now I want to look at the distribution of nonprofit industries in both places.

```{r}
barplot(table(boston$NTEE1))
barplot(table(dallas$NTEE1))
names(boston)
```
Bielefeld and Murdoch (2004) looked at industry B90 (Educational Support Services), and found that Boston had a negative response to nearby nonprofits while Dallas/Fort Worth had a positive response. I will get gamma for this industry for both metro areas and see if it confirms their results. 
```{r}
industries <- aggregate(boston$P1TOTREV, 
          list(boston$NTEECC),
          sum)
colnames(industries) <- c("Industry", "r")

library(plyr)
np <- count(boston, "NTEECC")
names(np)[1] = "Industry"
industries <- merge(industries, np)

#Subsetting the industries which have more than 1 nonprofit
industries <- subset.data.frame(industries, industries$freq > 1)

boston$subtotals <- industries$r[ match(boston$NTEECC, industries$Industry) ]
boston$zsubk <- boston$P1TOTREV/boston$subtotals
```
Looking at how many zipcodes actually have nonprofit revenue

```{r}
zips <- aggregate(boston$P1TOTREV,
                  list(boston$zipnew),
                  sum)
total <-sum(boston$P1TOTREV)
zips$share <- zips$x/total
hist(zips$share)
```
Clearly, there are only three zipcodes of any importance in Boston, as far as nonprofit revenue. I'm going to use only these three zipcodes, which are 02105, 02206, and 02210. I should get a positive gamma if I do this.
```{r}
areas <- aggregate(boston$P1TOTREV,
                       list(boston$zipnew, boston$ntmaj12),
                       sum)
colnames(areas) <- c("area", "sector", "subtotal")

areas <- subset.data.frame(areas, areas$area == "2105" | areas$area == "2206" | areas$area == "2210")

sectortotals <- aggregate(boston$P1TOTREV,
                       list(boston$ntmaj12),
                       sum)
colnames(sectortotals) <- c("sector", "sectortotal")
areas <- merge(areas, sectortotals, all = TRUE)
areas$xsubi <- areas$subtotal/areas$sectortotal
areas2 <- aggregate(boston$zsubk, 
                      list(boston$zipnew, boston$NTEECC),
                      sum)
colnames(areas2) <- c("area", "industry", "ssubi")
#Subsetting again before I merge.
areas2 <- subset.data.frame(areas2, areas2$area == "2105" | areas2$area == "2206" | areas2$area == "2210")

areas2$sector <- boston$ntmaj12[ match(areas2$industry, boston$NTEECC)]
areas <- merge(areas, areas2, by=c("area", "sector"))
#Now I have many ssubis which are NA, I want to make them 0.
areas[is.na(areas)] <- 0


areas$geocon <- (areas$ssubi-areas$xsubi)^2
Gbyindustry <- aggregate(areas$geocon, 
              list(areas$industry),
              sum)
colnames(Gbyindustry) <- c("Industry", "G")
#I will use Gbyindustry to subset boston at the very beginning.
industries2 <- merge(industries, Gbyindustry, all = FALSE)
H <- by(boston$zsubk, list(boston$NTEECC), function(x) sum(x^2), simplify = FALSE)
H <- cbind(H)
H <- unlist(H)
#This is where I get stuck, since H and industries are different lengths...
industries <- cbind(industries, H)
X <- by(areas$xsubi, list(areas$industry), function(x) sum(x^2), simplify = FALSE)
X <- cbind(X)
X <- unlist(X)
industries <- cbind(industries, X)
industries$gamma <- (industries$G-(1-industries$X)*industries$H)/((1-industries$X)*(1-industries$H))

bostongammas <- industries
plot(bostongammas$gamma, bostongammas$freq)

```
And now for Dallas:

```{r}
industries <- aggregate(dallas$P1TOTREV, 
          list(dallas$NTEECC),
          sum)
colnames(industries) <- c("Industry", "r")
dallas$subtotals <- industries$r[ match(dallas$NTEECC, industries$Industry) ]
dallas$zsubk <- dallas$P1TOTREV/dallas$subtotals
areas <- aggregate(dallas$P1TOTREV,
                       list(dallas$zipnew, dallas$ntmaj12),
                       sum)
colnames(areas) <- c("area", "sector", "subtotal")
sectortotals <- aggregate(dallas$P1TOTREV,
                       list(dallas$ntmaj12),
                       sum)
colnames(sectortotals) <- c("sector", "sectortotal")
areas <- merge(areas, sectortotals, all = TRUE)
areas$xsubi <- areas$subtotal/areas$sectortotal
areas2 <- aggregate(dallas$zsubk, 
                      list(dallas$zipnew, dallas$NTEECC),
                      sum)
colnames(areas2) <- c("area", "industry", "ssubi")
areas2$sector <- dallas$ntmaj12[ match(areas2$industry, dallas$NTEECC)]
areas <- merge(areas, areas2, by=c("area", "sector"))
areas$geocon <- (areas$ssubi-areas$xsubi)^2
Gbyindustry <- aggregate(areas$geocon, 
              list(areas$industry),
              sum)
colnames(Gbyindustry) <- c("Industry", "G")
industries <- merge(industries, Gbyindustry, all = TRUE)
H <- by(dallas$zsubk, list(dallas$NTEECC), function(x) sum(x^2), simplify = FALSE)
H <- cbind(H)
H <- unlist(H)
industries <- cbind(industries, H)
X <- by(areas$xsubi, list(areas$industry), function(x) sum(x^2), simplify = FALSE)
X <- cbind(X)
X <- unlist(X)
industries <- cbind(industries, X)
industries$gamma <- (industries$G-(1-industries$X)*industries$H)/((1-industries$X)*(1-industries$H))
library(plyr)
np <- count(dallas, "NTEECC")
names(np)[1] = "Industry"
industries <- merge(industries, np)
dallasgammas <- industries
plot(dallasgammas$gamma, dallasgammas$freq)
```

Interestingly, neither of these metro areas seem to have \textit{any} nonprofits in the B90 industry, so I'm not sure what's happening there. However, we do have an interesting distribution of gammas. 
```{r}
library(ggplot2)
bostonzip <- ggplot(data = bostongammas, aes(x=gamma)) + 
  geom_histogram(binwidth = .1, fill="black", col="gray") +
  xlim(-1, 1) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line = element_line(colour = "black"), text = element_text(size=20), plot.title = element_text(hjust = 0.5)) + labs(title = "Boston gammas at zipcode level", x = "Gamma", y = "Number of industries")
bostonzip
ggsave("boston99.jpg", width = 16, height = 9)

dallaszip <- ggplot(data = dallasgammas, aes(x=gamma)) + 
  geom_histogram(binwidth = .1, fill="black", col="gray") +
  xlim(-1, 1) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"), text = element_text(size=20), plot.title = element_text(hjust = 0.5)) + labs(title = "Dallas gammas at zipcode level", x = "Gamma", y = "Number of industries")
dallaszip
ggsave("dallas99.jpg", width = 16, height = 9)

```
```

