---
title: "Boston 1999"
output:
  pdf_document: default
  html_notebook: default
---
In this document I will analyze the agglomeration of nonprofit industries in Boston and Dallas/Ft. Worth and compare them to Bielefeld and Murdoch's (2004) results.
```{r}
load("/home/samutavi/Documents/Coe College/Spellman 2018/RData/US1999.Rdata")
boston <- subset.data.frame(US1999, US1999$CITY == "BOSTON" & US1999$STATE == "MA")
dallas <- subset.data.frame(US1999, US1999$CITY == "DALLAS" | US1999$CITY == "FORT WORTH" & US1999$STATE == "TX")
```
Now I want to look at the distribution of nonprofit industries in both places.

```{r}
barplot(table(boston$NTEE1))
barplot(table(dallas$NTEE1))
names(boston)
```
Bielefeld and Murdoch (2004) looked at industry B90 (Educational Support Services), and found that Boston had a negative response to nearby nonprofits while Dallas/Fort Worth had a positive response. I will get gamma for this industry for both metro areas and see if it confirms their results. 
```{r}
industries <- aggregate(boston$TOTREV, 
          list(boston$NTEECC),
          sum)
colnames(industries) <- c("Industry", "r")
boston$subtotals <- industries$r[ match(boston$NTEECC, industries$Industry) ]
boston$zsubk <- boston$TOTREV/boston$subtotals
areas <- aggregate(boston$TOTREV,
                       list(boston$ZIP5, boston$NTMAJ12),
                       sum)
colnames(areas) <- c("area", "sector", "subtotal")
sectortotals <- aggregate(boston$TOTREV,
                       list(boston$NTMAJ12),
                       sum)
colnames(sectortotals) <- c("sector", "sectortotal")
areas <- merge(areas, sectortotals, all = TRUE)
areas$xsubi <- areas$subtotal/areas$sectortotal
areas2 <- aggregate(boston$zsubk, 
                      list(boston$ZIP5, boston$NTEECC),
                      sum)
colnames(areas2) <- c("area", "industry", "ssubi")
areas2$sector <- boston$NTMAJ12[ match(areas2$industry, boston$NTEECC)]
areas <- merge(areas, areas2, by=c("area", "sector"))
areas$geocon <- (areas$ssubi-areas$xsubi)^2
Gbyindustry <- aggregate(areas$geocon, 
              list(areas$industry),
              sum)
colnames(Gbyindustry) <- c("Industry", "G")
industries <- merge(industries, Gbyindustry, all = TRUE)
H <- by(boston$zsubk, list(boston$NTEECC), function(x) sum(x^2), simplify = FALSE)
H <- cbind(H)
H <- unlist(H)
industries <- cbind(industries, H)
X <- by(areas$xsubi, list(areas$industry), function(x) sum(x^2), simplify = FALSE)
X <- cbind(X)
X <- unlist(X)
industries <- cbind(industries, X)
industries$gamma <- (industries$G-(1-industries$X)*industries$H)/((1-industries$X)*(1-industries$H))
library(plyr)
np <- count(boston, "NTEECC")
names(np)[1] = "Industry"
industries <- merge(industries, np)
bostongammas <- industries
plot(bostongammas$gamma, bostongammas$freq)

```
And now for Dallas:

```{r}
industries <- aggregate(dallas$TOTREV, 
          list(dallas$NTEECC),
          sum)
colnames(industries) <- c("Industry", "r")
dallas$subtotals <- industries$r[ match(dallas$NTEECC, industries$Industry) ]
dallas$zsubk <- dallas$TOTREV/dallas$subtotals
areas <- aggregate(dallas$TOTREV,
                       list(dallas$ZIP5, dallas$NTMAJ12),
                       sum)
colnames(areas) <- c("area", "sector", "subtotal")
sectortotals <- aggregate(dallas$TOTREV,
                       list(dallas$NTMAJ12),
                       sum)
colnames(sectortotals) <- c("sector", "sectortotal")
areas <- merge(areas, sectortotals, all = TRUE)
areas$xsubi <- areas$subtotal/areas$sectortotal
areas2 <- aggregate(dallas$zsubk, 
                      list(dallas$ZIP5, dallas$NTEECC),
                      sum)
colnames(areas2) <- c("area", "industry", "ssubi")
areas2$sector <- dallas$NTMAJ12[ match(areas2$industry, dallas$NTEECC)]
areas <- merge(areas, areas2, by=c("area", "sector"))
areas$geocon <- (areas$ssubi-areas$xsubi)^2
Gbyindustry <- aggregate(areas$geocon, 
              list(areas$industry),
              sum)
colnames(Gbyindustry) <- c("Industry", "G")
industries <- merge(industries, Gbyindustry, all = TRUE)
H <- by(dallas$zsubk, list(dallas$NTEECC), function(x) sum(x^2), simplify = FALSE)
H <- cbind(H)
H <- unlist(H)
industries <- cbind(industries, H)
X <- by(areas$xsubi, list(areas$industry), function(x) sum(x^2), simplify = FALSE)
X <- cbind(X)
X <- unlist(X)
industries <- cbind(industries, X)
industries$gamma <- (industries$G-(1-industries$X)*industries$H)/((1-industries$X)*(1-industries$H))
library(plyr)
np <- count(dallas, "NTEECC")
names(np)[1] = "Industry"
industries <- merge(industries, np)
dallasgammas <- industries
plot(dallasgammas$gamma, dallasgammas$freq)
```
 
```{r}
library(ggplot2)
bostonzip <- ggplot(data = bostongammas, aes(x=gamma)) + 
  geom_histogram(binwidth = .1, fill="black", col="gray") + 
  xlim(-5, 5) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line = element_line(colour = "black"), text = element_text(size=20), plot.title = element_text(hjust = 0.5)) + labs(title = "Boston gammas at zipcode level", x = "Gamma", y = "Number of industries")
bostonzip
ggsave("boston99.jpg", width = 16, height = 9)

dallaszip <- ggplot(data = dallasgammas, aes(x=gamma)) + 
  geom_histogram(binwidth = .1, fill="black", col="gray") +
  xlim(-5, 5) + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"), text = element_text(size=20), plot.title = element_text(hjust = 0.5)) + labs(title = "Dallas gammas at zipcode level", x = "Gamma", y = "Number of industries")
dallaszip
ggsave("dallas99.jpg", width = 16, height = 9)

```
I really want to know what percentage of observations are within a given range for Boston and Dallas.
```{r}
length(bostongammas$gamma[bostongammas$gamma < 5 & bostongammas$gamma > -5])/length(bostongammas$gamma)
```
```{r}
length(dallasgammas$gamma[dallasgammas$gamma < 5 & dallasgammas$gamma > -5])/length(dallasgammas$gamma)

```
```{r}
bostonzip
```
```{r}
dallaszip
```