---
title: "DGS Metric, Part 2"
output:
  pdf_document: default
  html_notebook: default
---
In this document, I will recreate the EG metric and the DGS metric for nonprofits in Cedar Rapids, to be able to compare them. First, I will bring in the East15 data file and isolate the nonprofits in Cedar Rapids. 
```{r}
load("/home/samutavi/Documents/Coe College/Spellman 2018/RData/East15.Rdata")
CR15 <- subset.data.frame(East15, East15$CITY=="CEDAR RAPIDS")
rm(East15)
```

Now I need to run two analyses. The first is to get the EG metric, gamma.

```{r}
industries <- aggregate(CR15$TOTREV, 
          list(CR15$NTEE1),
          sum)
colnames(industries) <- c("Industry", "r")
#Generating frequency column
library(plyr)
np <- count(CR15, "NTEE1")
names(np)[1] = "Industry"
industries <- merge(industries, np)
#Subsetting by frequency greater than 2
industries <- subset.data.frame(industries, freq > 2)

CR15$subtotals <- industries$r[ match(CR15$NTEE1, industries$Industry) ]
CR15$zsubk <- CR15$TOTREV/CR15$subtotals
areas <- aggregate(CR15$TOTREV,
                       list(CR15$ZIP, CR15$NTMAJ5),
                       sum)
colnames(areas) <- c("area", "sector", "subtotal")
sectortotals <- aggregate(CR15$TOTREV,
                       list(CR15$NTMAJ5),
                       sum)
colnames(sectortotals) <- c("sector", "sectortotal")
areas <- merge(areas, sectortotals, all = TRUE)
areas$xsubi <- areas$subtotal/areas$sectortotal
areas2 <- aggregate(CR15$zsubk, 
                      list(CR15$ZIP, CR15$NTEE1),
                      sum)
colnames(areas2) <- c("area", "industry", "ssubi")
areas2$sector <- CR15$NTMAJ5[ match(areas2$industry, CR15$NTEE1)]
areas <- merge(areas, areas2, by=c("area", "sector"))
areas$geocon <- (areas$ssubi-areas$xsubi)^2
Gbyindustry <- aggregate(areas$geocon, 
              list(areas$industry),
              sum)
colnames(Gbyindustry) <- c("Industry", "G")
industries <- merge(industries, Gbyindustry, all = TRUE)
H <- by(CR15$zsubk, list(CR15$NTEE1), function(x) sum(x^2), simplify = FALSE)
H <- cbind(H)
H <- unlist(H)
industries <- cbind(industries, H)
X <- by(areas$xsubi, list(areas$industry), function(x) sum(x^2), simplify = FALSE)
X <- cbind(X)
X <- unlist(X)
industries <- cbind(industries, X)
industries$gamma <- (industries$G-(1-industries$X)*industries$H)/((1-industries$X)*(1-industries$H))
NTEE1zip <- industries

```

I have almost entirely negative values for gamma, so it will be interesting to see how the DGS metric turns out. Now to get J-H:
```{r}
NTEE1 <- aggregate(CR15$TOTREV, 
          list(CR15$NTEE1),
          sum)
colnames(NTEE1) <- c("NTEE1", "r")

#Generating frequency column
library(plyr)
np <- count(CR15, "NTEE1")
names(np)[1] = "NTEE1"
NTEE1 <- merge(NTEE1, np)
colnames(NTEE1) <- c("NTEE1", "r", "N")


regions <- aggregate(CR15$TOTREV, 
          list(CR15$NTEE1, CR15$ZIP),
          sum)
colnames(regions) <- c("NTEE1", "ZIP", "r")

#Generating frequency column
rg <- count(regions, "NTEE1")
colnames(rg) <- c("NTEE1", "K")
NTEE1 <- merge(NTEE1, rg)

#Finding the max freq
max(rg$K)

CR15$IndRev <- NTEE1$r[ match(CR15$NTEE1, NTEE1$NTEE1)]
CR15$z_n <- CR15$TOTREV/CR15$IndRev
CR15$z_n2 <- CR15$z_n^2
H <- aggregate(CR15$z_n2,
                      list(CR15$NTEE1),
                      sum)
NTEE1$H <- H$x

regions$IndRev <- NTEE1$r[ match(regions$NTEE1, NTEE1$NTEE1)]
regions$s_k <- regions$r/regions$IndRev
regions$s_k2 <- regions$s_k^2
J <- aggregate(regions$s_k2,
                      list(regions$NTEE1),
                      sum)
NTEE1$J <- J$x

NTEE1$newJ <- NTEE1$J-(1/NTEE1$K)
NTEE1$newH <- NTEE1$H-(1/NTEE1$N)
NTEE1$newDGS <- NTEE1$newJ-NTEE1$newH


hist(NTEE1$newDGS)

```
Finally, I need to get gamma values and DGS values in the same dataframe to compare them.
```{r}
#Making a new dataframe with just the two variables I want.
agglom <- data.frame("Gamma" = NTEE1zip$gamma, "DGS" = NTEE1$newDGS)

#Making a plot first
plot(agglom$Gamma, agglom$DGS)

#Running the correlation
cor(agglom, use="complete.obs")

```

