---
title: "DGS Metric Replication"
output:
  pdf_document: default
  html_notebook: default
---
In this document, I will replicate the DGS metric for agglomeration. This is given as J-H, or  $$\sum_{k=1}^{K}{s_k^2}-\sum_{n=1}^{N}{z_n^2}$$ when N<K. The variables I need are:

$s_k$, the kth region's share of industry size

$z_n$, the nth firm's share of industry size.

Applying this to the nonprofit sector, I will use nonprofits as firms, total revenue as a measure of size, and zipcodes as regions. I will then be able to compare my results to the gammas we found as a replication of the EG metric.

First, I load the nonprofit data for all 501(c)(3) organizations in the 31 eastern states of the US.
```{r}
load("/home/samutavi/Documents/Coe College/Spellman 2018/RData/East15.Rdata")
```

I want to check that N<K so that the results are accurate. To do this, I will find the core code with the highest frequency, and compare that to the number of zipcodes for which we have nonprofit data.

```{r}
NTEECC <- aggregate(East15$TOTREV, 
          list(East15$NTEECC),
          sum)
colnames(NTEECC) <- c("NTEECC", "r")

#Generating frequency column
library(plyr)
np <- count(East15, "NTEECC")
names(np)[1] = "NTEECC"
NTEECC <- merge(NTEECC, np)
colnames(NTEECC) <- c("NTEECC", "r", "N")


#Finding the max freq
max(NTEECC$N)
NTEECC$NTEECC[which(NTEECC$N == "27776")]
```
So the highest N= 27776 in core code T20 and all other core codes are smaller than that. Now to find the highest K.
```{r}
regions <- aggregate(East15$TOTREV, 
          list(East15$NTEECC, East15$ZIP5),
          sum)
colnames(regions) <- c("NTEECC", "ZIP5", "r")

#Generating frequency column
rg <- count(regions, "NTEECC")
colnames(rg) <- c("NTEECC", "K")
NTEECC <- merge(NTEECC, rg)

#Finding the max freq
max(rg$K)

```
Now I have N and K for every NTEE core code. I want to double check that these numbers are correct. I will test a couple of codes.
```{r}
#Testing CC A013: N=13, K=13
East15$ZIP5[which(East15$NTEECC == "A013")]
```

This seems to be correct, but the dataframe NTEECC also shows that N is necessarily equal to or greater than K, if K is defined as the number of regions where the core code exists. Regardless of this, I am going to continue calculating the metric.

For $z_n$, I will add the core code revenue to East15, and then calculate each nonprofit's share of its core code revenue.
```{r}
East15$IndRev <- NTEECC$r[ match(East15$NTEECC, NTEECC$NTEECC)]
East15$z_n <- East15$TOTREV/East15$IndRev
East15$z_n2 <- East15$z_n^2
H <- aggregate(East15$z_n2,
                      list(East15$NTEECC),
                      sum)
NTEECC$H <- H$x
```
The next variable I need is the s_k for every region of every core code. This is each zip5's share of core code revenue, the same IndRev I used for H.
```{r}
regions$IndRev <- NTEECC$r[ match(regions$NTEECC, NTEECC$NTEECC)]
regions$s_k <- regions$r/regions$IndRev
regions$s_k2 <- regions$s_k^2
J <- aggregate(regions$s_k2,
                      list(regions$NTEECC),
                      sum)
NTEECC$J <- J$x
#Final step:
NTEECC$DGS <- NTEECC$J-NTEECC$H
```
Now to look at the distribution of the DGS metric.
```{r}
library(ggplot2)
ggplot(NTEECC, aes(x=DGS)) + 
  geom_histogram(binwidth = .01, fill="black", col="gray") +
  xlim(-1, 1) +
  ylim(0, 5) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
                        panel.background = element_blank(), axis.line = element_line(colour = "black"), text = element_text(size=20), plot.title = element_text(hjust = 0.5)) + labs(x = "DGS", y = "Frequency")
  
```

The vast majority of the values are 0. A handful of industries have small positive values. This is not surprising considering the construction of the metric. There seems to be no way for the metric to be negative. 

Next, I'm going to try the fix given in the paper where $1/N$ is subtracted from H and $1/K$ is subtracted from J before taking the difference.
```{r}
NTEECC$newJ <- NTEECC$J-(1/NTEECC$K)
NTEECC$newH <- NTEECC$H-(1/NTEECC$N)
NTEECC$newDGS <- NTEECC$newJ-NTEECC$newH


hist(NTEECC$newDGS)
```
I'm very interested in seeing how this measure correlates with the EG metric, gamma. I will load the dataframe that contains gamma and run a correlation on the two measures.
```{r}
load("/home/samutavi/Documents/Coe College/Spellman 2018/RData/NTEECCzip.Rdata")

#Making a new dataframe with just the two variables I want.
agglom <- data.frame("Gamma" = NTEECCzip$gamma, "DGS" = NTEECC$newDGS)

#Making a plot first
plot(agglom$Gamma, agglom$DGS, xlab = "Gamma", ylab = "Alpha")
ggplot(agglom, aes(Gamma, DGS))+
  geom_point() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"), text = element_text(size=20), plot.title = element_text(hjust = 0.5)) + labs(x = "Gamma", y = "Alpha")
ggsave("Output/gammaalpha.jpg", width = 16, height = 9)


#Running the correlation
cor(agglom, use="pairwise.complete.obs")
```

It looks like there is a strong correlation for positive values. I want to see how strong that is.
```{r}
#First, I will make a new dataframe with only positive values.
agglom$DGS[agglom$DGS < 0] <- NA
agglom$Gamma[agglom$Gamma <0] <- NA

#I want to see how many positive values I have for each metric.
length(agglom$Gamma[!is.na(agglom$Gamma)])
length(agglom$DGS[!is.na(agglom$DGS)])

#Now making a new df with only complete cases (no NAs anywhere).
agglom2 <- agglom[complete.cases(agglom), ]

#Running the correlation
cor(agglom2)

```

