---
title: "DGS Five Year Analysis"
output: html_notebook
---

In this document, I will replicate the DGS metric for nonprofits in the 31 eastern states for five different years. I will start with 2011.
```{r}
#load("RData/East11.Rdata")

Y2011 <- aggregate(East11$TOTREV, 
          list(East11$NTEECC),
          sum)
colnames(Y2011) <- c("NTEECC", "r")

#Generating frequency column
library(plyr)
np <- count(East11, "NTEECC")
names(np)[1] = "NTEECC"
Y2011 <- merge(Y2011, np)
colnames(Y2011) <- c("NTEECC", "r", "N")

regions <- aggregate(East11$TOTREV, 
          list(East11$NTEECC, East11$ZIP5),
          sum)
colnames(regions) <- c("NTEECC", "ZIP5", "r")

#Generating frequency column
rg <- count(regions, "NTEECC")
colnames(rg) <- c("NTEECC", "K")
Y2011 <- merge(Y2011, rg)

#Finding the max freq
max(rg$K)


East11$IndRev <- Y2011$r[ match(East11$NTEECC, Y2011$NTEECC)]
East11$z_n <- East11$TOTREV/East11$IndRev
East11$z_n2 <- East11$z_n^2
H <- aggregate(East11$z_n2,
                      list(East11$NTEECC),
                      sum)
Y2011$H <- H$x


regions$IndRev <- Y2011$r[ match(regions$NTEECC, Y2011$NTEECC)]
regions$s_k <- regions$r/regions$IndRev
regions$s_k2 <- regions$s_k^2
J <- aggregate(regions$s_k2,
                      list(regions$NTEECC),
                      sum)
Y2011$J <- J$x
#Final step:
Y2011$G <- Y2011$J-(1/Y2011$K)
Y2011$M <- Y2011$H-(1/Y2011$N)
Y2011$DGS2011 <- Y2011$G-Y2011$M

rm(East11)
```

Repeating this for 2012
```{r}
load("RData/East12.Rdata")

Y2012 <- aggregate(East12$TOTREV, 
          list(East12$NTEECC),
          sum)
colnames(Y2012) <- c("NTEECC", "r")

#Generating frequency column
library(plyr)
np <- count(East12, "NTEECC")
names(np)[1] = "NTEECC"
Y2012 <- merge(Y2012, np)
colnames(Y2012) <- c("NTEECC", "r", "N")

regions <- aggregate(East12$TOTREV, 
          list(East12$NTEECC, East12$ZIP5),
          sum)
colnames(regions) <- c("NTEECC", "ZIP5", "r")

#Generating frequency column
rg <- count(regions, "NTEECC")
colnames(rg) <- c("NTEECC", "K")
Y2012 <- merge(Y2012, rg)

#Finding the max freq
max(rg$K)


East12$IndRev <- Y2012$r[ match(East12$NTEECC, Y2012$NTEECC)]
East12$z_n <- East12$TOTREV/East12$IndRev
East12$z_n2 <- East12$z_n^2
H <- aggregate(East12$z_n2,
                      list(East12$NTEECC),
                      sum)
Y2012$H <- H$x


regions$IndRev <- Y2012$r[ match(regions$NTEECC, Y2012$NTEECC)]
regions$s_k <- regions$r/regions$IndRev
regions$s_k2 <- regions$s_k^2
J <- aggregate(regions$s_k2,
                      list(regions$NTEECC),
                      sum)
Y2012$J <- J$x
#Final step:
Y2012$G <- Y2012$J-(1/Y2012$K)
Y2012$M <- Y2012$H-(1/Y2012$N)
Y2012$DGS2012 <- Y2012$G-Y2012$M

rm(East12)
```
Now for 2013.


```{r}
load("RData/East13.Rdata")

Y2013 <- aggregate(East13$TOTREV, 
          list(East13$NTEECC),
          sum)
colnames(Y2013) <- c("NTEECC", "r")

#Generating frequency column
library(plyr)
np <- count(East13, "NTEECC")
names(np)[1] = "NTEECC"
Y2013 <- merge(Y2013, np)
colnames(Y2013) <- c("NTEECC", "r", "N")

regions <- aggregate(East13$TOTREV, 
          list(East13$NTEECC, East13$ZIP5),
          sum)
colnames(regions) <- c("NTEECC", "ZIP5", "r")

#Generating frequency column
rg <- count(regions, "NTEECC")
colnames(rg) <- c("NTEECC", "K")
Y2013 <- merge(Y2013, rg)

#Finding the max freq
max(rg$K)


East13$IndRev <- Y2013$r[ match(East13$NTEECC, Y2013$NTEECC)]
East13$z_n <- East13$TOTREV/East13$IndRev
East13$z_n2 <- East13$z_n^2
H <- aggregate(East13$z_n2,
                      list(East13$NTEECC),
                      sum)
Y2013$H <- H$x


regions$IndRev <- Y2013$r[ match(regions$NTEECC, Y2013$NTEECC)]
regions$s_k <- regions$r/regions$IndRev
regions$s_k2 <- regions$s_k^2
J <- aggregate(regions$s_k2,
                      list(regions$NTEECC),
                      sum)
Y2013$J <- J$x
#Final step:
Y2013$G <- Y2013$J-(1/Y2013$K)
Y2013$M <- Y2013$H-(1/Y2013$N)
Y2013$DGS2013 <- Y2013$G-Y2013$M

rm(East13)

```

2014:

```{r}
load("RData/East14.Rdata")

Y2014 <- aggregate(East14$TOTREV, 
          list(East14$NTEECC),
          sum)
colnames(Y2014) <- c("NTEECC", "r")

#Generating frequency column
library(plyr)
np <- count(East14, "NTEECC")
names(np)[1] = "NTEECC"
Y2014 <- merge(Y2014, np)
colnames(Y2014) <- c("NTEECC", "r", "N")

regions <- aggregate(East14$TOTREV, 
          list(East14$NTEECC, East14$ZIP5),
          sum)
colnames(regions) <- c("NTEECC", "ZIP5", "r")

#Generating frequency column
rg <- count(regions, "NTEECC")
colnames(rg) <- c("NTEECC", "K")
Y2014 <- merge(Y2014, rg)

#Finding the max freq
max(rg$K)


East14$IndRev <- Y2014$r[ match(East14$NTEECC, Y2014$NTEECC)]
East14$z_n <- East14$TOTREV/East14$IndRev
East14$z_n2 <- East14$z_n^2
H <- aggregate(East14$z_n2,
                      list(East14$NTEECC),
                      sum)
Y2014$H <- H$x


regions$IndRev <- Y2014$r[ match(regions$NTEECC, Y2014$NTEECC)]
regions$s_k <- regions$r/regions$IndRev
regions$s_k2 <- regions$s_k^2
J <- aggregate(regions$s_k2,
                      list(regions$NTEECC),
                      sum)
Y2014$J <- J$x
#Final step:
Y2014$G <- Y2014$J-(1/Y2014$K)
Y2014$M <- Y2014$H-(1/Y2014$N)
Y2014$DGS2014 <- Y2014$G-Y2014$M

rm(East14)


```

Finally, 2015:

```{r}
load("RData/East15.Rdata")

Y2015 <- aggregate(East15$TOTREV, 
          list(East15$NTEECC),
          sum)
colnames(Y2015) <- c("NTEECC", "r")

#Generating frequency column
library(plyr)
np <- count(East15, "NTEECC")
names(np)[1] = "NTEECC"
Y2015 <- merge(Y2015, np)
colnames(Y2015) <- c("NTEECC", "r", "N")

regions <- aggregate(East15$TOTREV, 
          list(East15$NTEECC, East15$ZIP5),
          sum)
colnames(regions) <- c("NTEECC", "ZIP5", "r")

#Generating frequency column
rg <- count(regions, "NTEECC")
colnames(rg) <- c("NTEECC", "K")
Y2015 <- merge(Y2015, rg)

#Finding the max freq
max(rg$K)


East15$IndRev <- Y2015$r[ match(East15$NTEECC, Y2015$NTEECC)]
East15$z_n <- East15$TOTREV/East15$IndRev
East15$z_n2 <- East15$z_n^2
H <- aggregate(East15$z_n2,
                      list(East15$NTEECC),
                      sum)
Y2015$H <- H$x


regions$IndRev <- Y2015$r[ match(regions$NTEECC, Y2015$NTEECC)]
regions$s_k <- regions$r/regions$IndRev
regions$s_k2 <- regions$s_k^2
J <- aggregate(regions$s_k2,
                      list(regions$NTEECC),
                      sum)
Y2015$J <- J$x
#Final step:
Y2015$G <- Y2015$J-(1/Y2015$K)
Y2015$M <- Y2015$H-(1/Y2015$N)
Y2015$DGS <- Y2015$G-Y2015$M

rm(East15)



```

Now I want to bind these together into one dataframe, but first I need to create the "YEAR" variable.

```{r}
#There's definitely a nicer way to do this with apply() or a function or something, but I don't know how to refer to df names :(
Y2011$YEAR <- "2011"
Y2012$YEAR <- "2012"
Y2013$YEAR <- "2013"
Y2014$YEAR <- "2014"
Y2015$YEAR <- "2015"

#Now I bind them together.
NPAGG <- rbind(Y2011, Y2012)
NPAGG <- rbind(NPAGG, Y2013)
NPAGG <- rbind(NPAGG, Y2014)
NPAGG <- rbind(NPAGG, Y2015)

#Creating a Group variable
NPAGG$Group <- substr(NPAGG$NTEECC, 1, 1)

save(NPAGG, file = "Output/NPAGG.RData")
```

The dataframe NPAGG now has all the values of the DGS metric (as well as all the variables involved) for every NP core code for every year from 2011 to 2015. In the next document, I will create visualizations of the values in this dataframe.
