---
title: "Replication of the EG Metric-Part 2"
output:
  pdf_document: default
  html_notebook: default
  toc: true
---
#Purpose
In this document, I want to replicate the EG metric for agglomeration for every nonprofit industry in the HU (Human Services) sector, in Cedar Rapids.
```{r}
load("/home/samutavi/Documents/Coe College/Spellman 2018/CR13.Rdata")
names(CR13)
```

#Method
I'm going to continue using total revenue as a measure of size and I will use 5-digit zip codes for geographic units. 

$i$ will be given by 5-digit zip codes.

$z_k$ is each NP establishment's share of total "ntee1" industry revenue (that is, the one-letter industry designation)

$x_i$ is $i$'s share of "HU" revenue

With these three variables, we would find the following:

$s_i$ would be constructed from $z_k$, using only establishments inside $i$, for each one-letter industry

$G$ would be constructed from $s_i$ and $x_i$, for each one-letter industry

$H$ comes from a Herfindahl of $z_k$, for each one-letter industry

These variables would give $\gamma$, which is the EG measure of agglomeration. I want a gamma for every one-letter industry inside HU.

#Starting with HU sector
The HU sector has eight one-letter industries, I, J, K, L, M, N, O, and P. In Part 1, we found $\gamma$ for industry P. Now I want to automate the code to get gamma for every industry in sector HU.

I will use a subset of CR13 that is just HU establishments.

```{r}
HU <- subset(CR13, CR13$ntmaj5 == "HU")
barplot(table(HU$ntee1))
```
#Creating Necessary Variables

##Creating $z_k$
The first step is to create a variable called "zsubk" which is every nonprofit's share of total revenue in its own industry. First, I need a data set of revenue subtotals by "ntee1" industry.
```{r}
totrevnt1 <- aggregate(HU$totrev, 
          list(HU$ntee1),
          sum)
totrevnt1
```
Now I need to divide each nonprofit's total revenue by the appropriate number from the dataset above, depending on the NTEE1 industry. The easiest way to do this is probably to create a new column in HU that has the relevant subtotal for each nonprofit. 

```{r}
HU$subtotals <- totrevnt1$x[ match(HU$ntee1, totrevnt1$Group.1) ]

```

Next, I will create a vector "zsubk" which is each establishment's total revenue divided by the sum given above.
```{r}
HU$zsubk <- HU$totrev/HU$subtotals
HU$zsubk
sum(HU$zsubk) #Checking that the individual shares add to 8.
```
 
This gives $z_k$. 

##Creating $x_i$
Next, I want to find $x_i$ which is each zip code's share of total HU revenue. So first I find totrevHU.  
```{r}
totrevHU <- sum(HU$totrev)
totrevHU
```
I can use the aggregate command to add totrev by zip code.

```{r}
totrevzip <- aggregate(HU$totrev, 
          list(HU$zip5),
          sum)
totrevzip

```
Perfect. This has defined 11 areas ($i$) and now we can get $x_i$ for each of the areas by dividing each of the numbers above by totrevHU.

```{r}
totrevzip$xsubi <- totrevzip$x/totrevHU
totrevzip$xsubi
sum(totrevzip$xsubi)
```

##Creating $s_i$
Now I have $z_k$ and $x_i$. Using $z_k$, I need to get $s_i$ for every zip code. This is defined as $s_i=\sum_k{z_k}{u_{ki}}$ where $u_{ki}$ is an indicator variable equal to 1 if establishment $k$ is in $i$ and equal to 0 if $k$ is not in $i$. I need a different $s_i$ for every industry, so basically I need to aggregate just the establishments in each zipcode AND industry to find subtotals of the variable I've called "zsubk". 

```{r}
totrevzip2 <- aggregate(HU$zsubk, 
                      list(HU$zip5, HU$ntee1),
                      sum)
colnames(totrevzip2) <- c("Group.1", "Group.2", "ssubi")
sum(totrevzip2$ssubi)
sum(totrevzip2$ssubi[totrevzip2$Group.2 == "P"]) #Checking that each industry totals to 1.
```
```{r}
#Checking that there are no values of ssubi that are above 1.
length(totrevzip2$ssubi)
length(totrevzip2$ssubi[totrevzip2$ssubi > 1])
sum(totrevzip2$ssubi)
```

##Finding $G$ for Industry P
Now I add these "ssubi" values to the data frame "totrevzip" in a column called "ssubi". I use the merge function for this. I would like to get a value of 0 for all the zipcodes that have no revenue from P; I will do that in a separate command.
 
```{r}
revzip <- merge(totrevzip, totrevzip2, all = TRUE)
revzip[is.na(revzip)] <- 0

revzip

```
With this dataset, I can find G. $G=\sum_i{(s_i-x_i)^2}$

```{r}
revzip$geocon <- (revzip$ssubi-revzip$xsubi)^2
Gbyindustry <- aggregate(revzip$geocon, 
              list(revzip$Group.2),
              sum)
colnames(Gbyindustry) <- c("Group.1", "G")
totrevnt1 <- merge(totrevnt1, Gbyindustry, all = TRUE)
```
Now I have a vector of G values by industry, which is exactly what I want.

##Finding $H$ for Every Industry
Now I can use zsubk to find the Herfindahl index given by $H=\sum_k{z_k^2}$ for every industry.
```{r}
library(hhi)
?hhi
H <- by(HU, list(HU$ntee1), function(x) hhi(x, "zsubk"), simplify = FALSE)
#Now I need this as a dataframe.
H <- cbind(H)
H <- unlist(H)
totrevnt1 <- cbind(totrevnt1, H)

```
##Finding $X$ for Every Industry
The last thing I need in order to find $\gamma$ for every industry is $\sum{x_i^2}$, which I will just call "X". Again, I can use "by" to apply my function to subsets of the dataframe.

```{r}
X <- by(revzip$xsubi, list(revzip$Group.2), function(x) sum(x^2), simplify = FALSE)
X <- cbind(X)
X <- unlist(X)
totrevnt1 <- cbind(totrevnt1, X)
#To avoid confusion, I'm going to delete the column in totrevnt1 called "x" because this has nothing to do with "X".
totrevnt1$x <- NULL
```

#Result
Now I have G, H, and X by industry in a dataframe called totrevnt1. I can use those three to come up with $\gamma$, using the EG definition of $\gamma$.

$$\gamma=\frac{G-(1-\sum{x_i^2})H}{(1-\sum{x_i^2})(1-H)}$$
that is,
$$\gamma=\frac{G-(1-X)H}{(1-X)(1-H)}$$
```{r}
attach(totrevnt1)
totrevnt1$gamma <- (totrevnt1$G-(1-totrevnt1$X)*totrevnt1$H)/((1-totrevnt1$X)*(1-totrevnt1$H))
totrevnt1$gamma
```
This is a very interesting result, except that there are two values smaller than -1, which is an indication that something went wrong somewhere...Troubleshooting is needed at this point to make sure each variable is what it is supposed to be, because I have checked the final result for industry K by hand, and the results are correct, given the values in the dataframe. Therefore, the values in the dataframe must be wrong for one or more variables. 