---
title: "Replication of the EG Metric"
output:
  pdf_document: default
  html_notebook: default
  toc: true
---
#Purpose
In this document, I want to replicate the EG metric for agglomeration using sample data and variables that could be proxies for the variables used by Ellison and Glaeser.
```{r}
#install.packages("hhi")
load("/home/samutavi/Documents/Coe College/Spellman 2018/CR13.Rdata")
names(CR13)
```

#Method
I don't have employment data for the nonprofits in CR, so I'm considering using total revenue as a measure of size. The EG metric needs basically three variables, which would look like the following if we used revenue:

$i$ will be given by census tracts (to be constructed)

$z_k$ is each NP establishment's share of total "nteecc" industry revenue

$x_i$ is $i$'s share of "ntmaj5" revenue

With these three variables, we would find the following:

$s_i$ would be constructed from $z_k$, using only establishments inside $i$

$G$ would be constructed from $s_i$ and $X_i$

$H$ comes from a Herfindahl of $z_k$

These variables would give $\gamma$, which is the EG measure of agglomeration.

#Choosing a Test Industry
First, I'm interested in looking at the biggest categories in the NTEE major 5 groups.

```{r}
barplot(table(CR13$ntmaj5))
```

The Human Services group includes groups I, J, K, L, M, N, O, and P. So now I would like to see what sizes those groups are, using only a subset of the data that is HU establishments.

```{r}
HU <- subset(CR13, CR13$ntmaj5 == "HU")
barplot(table(HU$ntee1))
```

 Within P, let's look at the specific NTEE industries.
 
```{r}
P <-subset(HU, HU$ntee1 == "P")
barplot(table(P$nteecc))
```
 
The biggest group within P has only 5 establishments, which seems too small to be useful. Group P might be the most specific we can get within Cedar Rapids and even that might be too small a group, since there are only 31 establishments in CR. Anyway, as a test of the metric, we can try to use P as the industry, with HU as the larger group (i.e. "overall manufacturing"). Just for testing purposes, I will use zip codes since finding the census tract code for each establishment is a separate task.

#Creating Necessary Variables

##Creating $z_k$
In that case, I will create a variable called "zsubk" which is basically $z_k$, that is, the establishment's share of total revenue in P in CR. First, I need to find the total revenue for all P establishments in CR.

```{r}
totrevP <- sum(P$totrev)
totrevP
```

Next, I will create a vector "zsubk" which is each establishment's total revenue divided by the sum given above.
```{r}
P$zsubk <- P$totrev/totrevP
P$zsubk
sum(P$zsubk) #Checking that the individual shares add to 1, as they should.
```
 
This gives $z_k$. 

##Creating $x_i$
Next, I want to find $x_i$ which is each zip code's share of total HU revenue. So first I find totrevHU.  
```{r}
totrevHU <- sum(HU$totrev)
totrevHU
```
Finding each zip code's share is trickier. It turns out I can use the aggregate command to add totrev by zip code.

```{r}
?aggregate
totrevzip <- aggregate(HU$totrev, 
          list(HU$zip),
          sum)
totrevzip

#Added later to compare scale:
totrevzip5 <- aggregate(HU$totrev,
              list(HU$zip5),
              sum)
totrevzip5
```
Perfect. This has defined 79 areas ($i$) and now we can get $x_i$ for each of the areas by dividing each of the numbers above by totrevHU.

```{r}
names(totrevzip)
totrevzip$xsubi <- totrevzip$x/totrevHU
totrevzip$xsubi
sum(totrevzip$xsubi)

names(totrevzip5)
totrevzip5$xsubi <- totrevzip5$x/totrevHU
totrevzip5$xsubi
sum(totrevzip5$xsubi)
```

##Creating $s_i$
Now I have $z_k$ and $x_i$. Using $z_k$, I need to get $s_i$ for every zip code. This is defined as $s_i=\sum_k{z_k}{u_{ki}}$ where $u_{ki}$ is an indicator variable equal to 1 if establishment $k$ is in $i$ and equal to 0 if $k$ is not in $i$, so basically I need to aggregate just the establishments in each zipcode to find subtotals of the variable I've called "zsubk". 

```{r}
totrevzip2 <- aggregate(P$zsubk, 
                      list(P$zip),
                      sum)
colnames(totrevzip2) <- c("Group.1", "ssubi")
sum(totrevzip2$ssubi)

totrevzip52 <- aggregate(P$zsubk, 
                      list(P$zip5),
                      sum)
colnames(totrevzip52) <- c("Group.1", "ssubi")
sum(totrevzip52$ssubi)

```

##Finding $G$ for Industry P
Now the question is how to add these "x" values to the data frame "totrevzip" in a column called "ssubi". If the zip code is not in the list above, the value of ssubi should be 0 and if it is in the list above, it should put in the value of x above. I found that I can use the merge function for this. I would like to get a value of 0 for all the zipcodes that have no revenue from P, but maybe I will do that in a separate command.
 
```{r}
revzip <- merge(totrevzip, totrevzip2, all = TRUE)
revzip[is.na(revzip)] <- 0
revzip$x <- NULL  #removing a column I don't need
revzip

revzip5 <- merge(totrevzip5, totrevzip52, all = TRUE)
revzip5[is.na(revzip5)] <- 0
revzip5$x <- NULL  #removing a column I don't need
revzip5


```
With this dataset, I can find G. $G=\sum_i{(s_i-x_i)^2}$

```{r}
revzip$geocon <- (revzip$ssubi-revzip$xsubi)^2
G <- sum(revzip$geocon)
G

revzip5$geocon <- (revzip5$ssubi-revzip5$xsubi)^2
G5 <- sum(revzip5$geocon)
G5 

```

##Finding $H$ for Industry P
Now if I can use zsubk to find the Herfindahl index given by $H=\sum_k{z_k^2}$, I can apply the entire formula to find $\gamma$ for industry P. First, I will create a new column "zsubk2" which is expressed as percentages.
```{r}
P$zsubk2 <- P$zsubk*100 #Ended up not using this.
sum(P$zsubk2)
library(hhi)
?hhi
#I think this is the same in both scales.
```
```{r}
#Checking that there are no values of ssubi that are above 1.
length(totrevzip2$ssubi)
length(totrevzip2$ssubi[revzip$ssubi > 1])
sum(totrevzip2$ssubi)

length(totrevzip52$ssubi)
length(totrevzip52$ssubi[revzip5$ssubi > 1])
sum(totrevzip52$ssubi)

```

```{r}
H <- hhi(P, "zsubk") 
H
```

#Result
Now I have G, H, and $x_i$ for industry P. I can use those three to come up with $\gamma$, using the EG definition of $\gamma$.

$$\gamma=\frac{G-(1-\sum{x_i^2})H}{(1-\sum{x_i^2})(1-H)}$$

```{r}
sum(revzip$xsubi)
hhi(revzip, "xsubi")
gamma <- (G-H*(1-hhi(revzip, "xsubi")))/((1-hhi(revzip, "xsubi"))*(1-H))
gamma

sum(revzip5$xsubi)
hhi(revzip5, "xsubi")
gamma5 <- (G5-H*(1-hhi(revzip5, "xsubi")))/((1-hhi(revzip5, "xsubi"))*(1-H))
gamma5

```
This indicates that nonprofits in this industry are actually dispersing rather than agglomerating. I want to repeat this with 5-digit zipcodes and compare the two gammas, so that is my next step. I'm going back and adding a line of code to use "zip5" instead of "zip".

It turns out I get a similar result, indicating that the change in scale did not make much of a difference. That is definitely interesting since previous work has indicated that scale makes a big difference. The next step is to do the code again, this time making G, H, and $\gamma$ vectors with values for every industry in HU, and then other sectors.
