---
title: "East15MOD, Part 2"
output: html_notebook
---

In this document, I get the subsetted final dataset for the gamma analysis at the state level and create visuals for both CCzipFINAL and CCstateFINAL.

In Part 1, I created a dataset called CCzipFINAL, which was a subset of NTEECCzip. Now, using USEast15, Part 2, I will similarly get a new subsetted dataset called CCstateFINAL from the dataset called NTEECCstate.

```{r}
load("/home/samutavi/Documents/Coe College/Spellman 2018/RData/East15.Rdata")
source("~/Documents/Coe College/Spellman 2018/R/gazer.R")

#Remove negative revenues
mod1 <- subset.data.frame(East15, East15$TOTREV >= 0)

#Run analysis at the state level
industries <- aggregate(mod1$TOTREV, 
          list(mod1$NTEECC),
          sum)
colnames(industries) <- c("Industry", "r")
#Generating frequency column
library(plyr)
np <- count(mod1, "NTEECC")
names(np)[1] = "Industry"
industries <- merge(industries, np)
#Subsetting by frequency greater than 3
industries <- subset.data.frame(industries, freq > 2)

mod1$subtotals <- industries$r[ match(mod1$NTEECC, industries$Industry) ]
mod1$zsubk <- mod1$TOTREV/mod1$subtotals
areas <- aggregate(mod1$TOTREV,
                       list(mod1$STATE, mod1$NTMAJ12),
                       sum)
colnames(areas) <- c("area", "sector", "subtotal")
sectortotals <- aggregate(mod1$TOTREV,
                       list(mod1$NTMAJ12),
                       sum)
colnames(sectortotals) <- c("sector", "sectortotal")
areas <- merge(areas, sectortotals, all = TRUE)
areas$xsubi <- areas$subtotal/areas$sectortotal
areas2 <- aggregate(mod1$zsubk, 
                      list(mod1$STATE, mod1$NTEECC),
                      sum)
colnames(areas2) <- c("area", "industry", "ssubi")
areas2$sector <- mod1$NTMAJ12[ match(areas2$industry, mod1$NTEECC)]
areas <- merge(areas, areas2, by=c("area", "sector"))
areas$geocon <- (areas$ssubi-areas$xsubi)^2
Gbyindustry <- aggregate(areas$geocon, 
              list(areas$industry),
              sum)
colnames(Gbyindustry) <- c("Industry", "G")
industries <- merge(industries, Gbyindustry, all = TRUE)
H <- by(mod1$zsubk, list(mod1$NTEECC), function(x) sum(x^2), simplify = FALSE)
H <- cbind(H)
H <- unlist(H)
industries <- cbind(industries, H)
X <- by(areas$xsubi, list(areas$industry), function(x) sum(x^2), simplify = FALSE)
X <- cbind(X)
X <- unlist(X)
industries <- cbind(industries, X)
industries$gamma <- (industries$G-(1-industries$X)*industries$H)/((1-industries$X)*(1-industries$H))
CCstate <- industries
#save(NTEECCstate, file = "/home/samutavi/Documents/Coe College/Spellman 2018/RData/NTEECCstate.Rdata")

#Apply two criteria
CCstateFINAL <- subset(CCstate, CCstate$H <= .95 & CCstate$freq >= 5)
gazer(CCstateFINAL)
```

Something is strange here. G should not be above 1. I'm subsetting these to look at them more closely.

```{r}
badG <- subset.data.frame(CCstateFINAL, CCstateFINAL$G > 1)
badG
```

Looking at xsubi and ssubi for this industry...

```{r}
Q193 <- subset.data.frame(areas, areas$industry == "Q193")
Q <- subset.data.frame(East15, East15$NTEECC == "Q193")
```



Now I save this dataset in both the USEast15/Output folder and the main RData folder for Spellman 2018.
``{r}
save(CCstateFINAL, file = "/home/samutavi/Documents/Coe College/Spellman 2018/USEast2015/Output/CCstateFINAL.Rdata")

#Also save in the main Rdata folder
save(CCstateFINAL, file = "/home/samutavi/Documents/Coe College/Spellman 2018/RData/CCstateFINAL.Rdata")

```


