---
title: "East15 Modified"
output: html_notebook
---

In this document, I will rerun the analysis of agglomeration in nonprofits using a modified version of the East15 dataframe. I will then compare the distribution of gammas to the previous distribution.

```{r}
load("~/Documents/Coe College/Spellman 2018/RData/East15.Rdata")
source("~/Documents/Coe College/Spellman 2018/R/gazer.R")
```

#MOD 1: Remove negative revenues
Possible bias? Bad data or accounting identity?
```{r}
mod1 <- subset.data.frame(East15, East15$TOTREV >= 0)
```
Now to run the analysis:

```{r}
industries <- aggregate(mod1$TOTREV, 
          list(mod1$NTEECC),
          sum)
colnames(industries) <- c("Industry", "r")
#Generating frequency column
library(plyr)
np <- count(mod1, "NTEECC")
names(np)[1] = "Industry"
industries <- merge(industries, np)

#Subsetting by frequency greater than 3: should this be done later???
#industries <- subset.data.frame(industries, freq > 2)

mod1$subtotals <- industries$r[ match(mod1$NTEECC, industries$Industry) ]
mod1$zsubk <- mod1$TOTREV/mod1$subtotals
areas <- aggregate(mod1$TOTREV,
                       list(mod1$ZIP5, mod1$NTMAJ12),
                       sum)
colnames(areas) <- c("area", "sector", "subtotal")
sectortotals <- aggregate(mod1$TOTREV,
                       list(mod1$NTMAJ12),
                       sum)
colnames(sectortotals) <- c("sector", "sectortotal")
areas <- merge(areas, sectortotals, all = TRUE)
areas$xsubi <- areas$subtotal/areas$sectortotal
areas2 <- aggregate(mod1$zsubk, 
                list(mod1$ZIP5, mod1$NTEECC),
                sum)
colnames(areas2) <- c("area", "industry", "ssubi")
areas2$sector <- mod1$NTMAJ12[ match(areas2$industry, mod1$NTEECC)]
areas <- merge(areas, areas2, by=c("area", "sector"))
areas$geocon <- (areas$ssubi-areas$xsubi)^2
Gbyindustry <- aggregate(areas$geocon, 
              list(areas$industry),
              sum)
colnames(Gbyindustry) <- c("Industry", "G")
industries <- merge(industries, Gbyindustry, all = TRUE)
H <- by(mod1$zsubk, list(mod1$NTEECC), function(x) sum(x^2), simplify = FALSE)
H <- cbind(H)
H <- unlist(H)
industries <- cbind(industries, H)
X <- by(areas$xsubi, list(areas$industry), function(x) sum(x^2), simplify = FALSE)
X <- cbind(X)
X <- unlist(X)
industries <- cbind(industries, X)
industries$gamma <- (industries$G-(1-industries$X)*industries$H)/((1-industries$X)*(1-industries$H))
NTEECCmod1 <- industries
gazer(NTEECCmod1)
#save(NTEECCzip, file = "/home/samutavi/Documents/Coe College/Spellman 2018/RData/NTEECCzip.Rdata")
```
This gamma distribution still has large negative values. These are likely caused by H values close to 1. I will check this by looking at all large negative gammas.

```{r}
lows <- subset(NTEECCmod1,NTEECCmod1$gamma < -1)
gazer(lows)
```

All these low gammas are for core codes that have an H close to 1 and an X of basically 0. An H approaching 1 indicates that the majority of the revenue in the core code comes from just one nonprofit, since H is a measure of the "plant size distribution". An X=0 means no area contains a significant fraction of the sector revenue.

Based on what I have learned from the outliers, I think we should be looking only at core codes which satisfy 2 criteria:

1. They have an H less than some cutoff, suppose .95
2. They have a frequency of greater than some cutoff, suppose 5.
 
```{r}
CCzipFINAL <- subset(NTEECCmod1, NTEECCmod1$H <= .95 & NTEECCmod1$freq >= 5)
gazer(CCzipFINAL)
```

This distribution looks entirely reasonable, so I will save it as an Rdata file.

```{r}
save(CCzipFINAL, file = "/home/samutavi/Documents/Coe College/Spellman 2018/USEast2015/Output/CCzipFINAL.Rdata")

#Also save in the main Rdata folder
save(CCzipFINAL, file = "/home/samutavi/Documents/Coe College/Spellman 2018/RData/CCzipFINAL.Rdata")

```
Now I want to recreate the ggplot distributions of gamma at the zip level.

```{r}
library(ggplot2)
gammazipFINAL <- ggplot(data = CCzipFINAL, aes(x=gamma)) + 
  geom_histogram(binwidth = .01, fill="black", col="gray") +
  xlim(-1, 1)
#Takes out gridlines, background, and creates neater appearance
gammazipFINAL + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"), text = element_text(size=20), plot.title = element_text(hjust = 0.5)) + labs(title = "NP gamma at zipcode level", x = "Gamma", y = "Number of industries")
ggsave("gammazipFINAL.jpg", width = 16, height = 9)

```



#MOD 2: Remove nonprofits (outliers) with huge revenues
How much does revenue affect gammas? In this modification, I will run the analysis without the top 10% of revenues and see how much the gamma distribution changes.
```{r}
mean(East15$TOTREV)
median(East15$TOTREV)
```
To be continued...
