---
title: "EG Metric, Nonprofits in Eastern US, 2015-Part 2"
output:
  pdf_document: default
  html_notebook: default
  toc: true
---
#Purpose
In this document, I want to replicate the EG metric for every NTEE industry in the Eastern US, using state as the geographic unit. I hypothesize that at the state level, gammas are much more positive than they are at the zipcode level. I will use the same data set I used for Part 1, that is the 31 eastern states of the US.
```{r}
load("/home/samutavi/Documents/Coe College/Spellman 2018/RData/East15.Rdata")
```
My first step is to check that the file contains only states that I want to include.
```{r}
levels(East15$STATE)
```

Great! I think I have all the values I need then, to run the following code to get the values of all major variables and $\gamma$, the Ellison and Glaeser (1997) metric for agglomeration.

```{r}
industries <- aggregate(East15$TOTREV, 
          list(East15$NTEECC),
          sum)
colnames(industries) <- c("Industry", "r")
#Generating frequency column
library(plyr)
np <- count(East15, "NTEECC")
names(np)[1] = "Industry"
industries <- merge(industries, np)
#Subsetting by frequency greater than 3
industries <- subset.data.frame(industries, freq > 2)

East15$subtotals <- industries$r[ match(East15$NTEECC, industries$Industry) ]
East15$zsubk <- East15$TOTREV/East15$subtotals
areas <- aggregate(East15$TOTREV,
                       list(East15$STATE, East15$NTMAJ12),
                       sum)
colnames(areas) <- c("area", "sector", "subtotal")
sectortotals <- aggregate(East15$TOTREV,
                       list(East15$NTMAJ12),
                       sum)
colnames(sectortotals) <- c("sector", "sectortotal")
areas <- merge(areas, sectortotals, all = TRUE)
areas$xsubi <- areas$subtotal/areas$sectortotal
areas2 <- aggregate(East15$zsubk, 
                      list(East15$STATE, East15$NTEECC),
                      sum)
colnames(areas2) <- c("area", "industry", "ssubi")
areas2$sector <- East15$NTMAJ12[ match(areas2$industry, East15$NTEECC)]
areas <- merge(areas, areas2, by=c("area", "sector"))
areas$geocon <- (areas$ssubi-areas$xsubi)^2
Gbyindustry <- aggregate(areas$geocon, 
              list(areas$industry),
              sum)
colnames(Gbyindustry) <- c("Industry", "G")
industries <- merge(industries, Gbyindustry, all = TRUE)
H <- by(East15$zsubk, list(East15$NTEECC), function(x) sum(x^2), simplify = FALSE)
H <- cbind(H)
H <- unlist(H)
industries <- cbind(industries, H)
X <- by(areas$xsubi, list(areas$industry), function(x) sum(x^2), simplify = FALSE)
X <- cbind(X)
X <- unlist(X)
industries <- cbind(industries, X)
industries$gamma <- (industries$G-(1-industries$X)*industries$H)/((1-industries$X)*(1-industries$H))
NTEECCstate <- industries
save(NTEECCstate, file = "/home/samutavi/Documents/Coe College/Spellman 2018/RData/NTEECCstate.Rdata")
plot(industries$gamma, industries$freq)
```
```{r}
library(ggplot2)
gammastate <- ggplot(data = NTEECCstate, aes(x=gamma)) + 
  geom_histogram(binwidth = .01, fill="black", col="gray") +
  xlim(-1, 1)
#Takes out gridlines, background, and creates neater appearance
gammastate + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"), text = element_text(size=20), plot.title = element_text(hjust = 0.5))+ labs(title = "NP gamma at state level", x = "Gamma", y = "Number of industries")
ggsave("gammastate.jpg", width = 16, height = 9)
```
A little more information about the distribution:
```{r}
install.packages("fitdistrplus")
library(fitdistrplus)
descdist(industries$gamma[!is.na(industries$gamma)], discrete = FALSE)
```
