---
title: "EG Coagglomeration Metric"
output:
  pdf_document: default
  html_notebook: default
---
In this notebook, I will try to replicate the Ellison and Glaeser (1997) metrics of coagglomeration, $\gamma^c$ and $\lambda$. I start with the dataset of the 31 eastern states of the US.
```{r}
load("/home/samutavi/Documents/Coe College/Spellman 2018/RData/East15.Rdata")
```

The equation for $\gamma^c$ is:
$$\gamma^c=\frac{[\frac{G}{(1-X)}]-H-\sum_{j=1}^r{\hat\gamma_jw_j^2(1-H_j)}}{1-\sum_{j=1}^rw^2_j}$$
The variables I need to replicate $\gamma^c$ are:
\begin{enumerate}
  \item{G, the raw concentration of employment in the group as a whole}
  \item{H, the plant size Herfindahl of the group as a whole}
  \item{$X$, the Herfindahl of $x_i$, each area's share of overall manufacturing employment}
  \item{$\hat\gamma_j$, the gamma of the jth industry in the group}
  \item{$w_j$, the jth industry's employment share of the group}
  \item{$H_j$, the plant size Herfindahl of the jth industry}
\end{enumerate}

Several of these come directly from the agglomeration metric, $\gamma$. Specifically, $\hat\gamma_j$ is $\gamma$ from the previous analysis, $X$ is the same as the previous $X$, and $H_j$ is the same as $H$ in the previous analysis. The $G$ and $H$ I can get from a previous analysis at the NTEE1 level. So really the only new variable is $w_j$. 

Of course, we are using total revenue instead of employment, and our industry "groups" will initially be the single letter NTEE1 industry classification. The $\gamma^c$ metric should then tell us how much nonprofit industries cluster with similar industries. A second step might be to find ways to relate different industries (for example by upstream and downstream ties) to see whether pairs of different industries cluster together at all.

My first step will be to bring in all the variables that I already have from the previous analysis and to rename them for this one.

```{r}
load("/home/samutavi/Documents/Coe College/Spellman 2018/RData/NTEECCzip.Rdata")
colnames(NTEECCzip) <- c("Industry", "r", "Gsubj", "Hsubj", "X", "gammahat", "freq")
```

The next step is to find the "new" variable $w_j$, which all relates to the group, which in this case is the NTEE1 classification.

#Finding $w_j$
This variable should be fairly easy to get. I already have "r", which is each industry's total revenue. I now need to divide this by the group's total revenue, which I can get from the East15 dataset. So first, I'm going to create a new dataframe called "Coagg" which has the three variables I already have and columns for the new one I need.
```{r}
coagg <- data.frame(NTEECCzip$Industry, NTEECCzip$Hsubj, NTEECCzip$X, NTEECCzip$gammahat, NTEECCzip$r)
colnames(coagg) <- c("Industry", "Hsubj", "X", "gammahat", "revenue")
#Erasing a column that is misleading; this is not the X I need.
coagg$X <- NULL
#Creating a list of NTEE1 revenue.
Group <- aggregate(East15$TOTREV, 
          list(East15$NTEE1),
          sum)
colnames(Group) <- c("Group", "grprev")
#Adding a "Group" column to coagg dataframe.
coagg$Group <- East15$NTEE1[ match(coagg$Industry, East15$NTEECC)]
#Merging dataframes by Group
coagg <- merge(coagg, Group, all = TRUE)
#Creating wsubj
coagg$wsubj <- coagg$revenue/coagg$grprev
```

#Finding H
Next I will get H for each group, that is, each NTEE1 category. $H=\sum_j{w_j^2H_j}$ so I just create a new column in the coagg dataframe and aggregate the values by group. 
```{r}
#Formula applied
coagg$addforH <- coagg$wsubj^2*coagg$Hsubj
#Subtotals added by group, excluding all NaNs.
H <- aggregate(coagg$addforH[!is.nan(coagg$addforH)],
                     list(coagg$Group[!is.nan(coagg$addforH)]),
                     sum)
colnames(H) <- c("Group", "H")
#Merge with coagg (and Group, just for future reference) by Group
Group <- merge(Group, H, all = T)
coagg <- merge(coagg, H, all = T)
```
I'm going to clean up the coagg dataframe by deleting a few unnecessary columns.
```{r}
coagg$revenue <- NULL
coagg$grprev <- NULL
coagg$addforH <- NULL
Group$grprev <- NULL
```

#Finding G
The last variable I need is G for each group. $G=\sum(s_i-x_i)^2$ where $s_i$ is area $i$'s share of total revenue in the group and $x_i$ is $i$'s share of total revenue in the sector. This is easy because I actually have G for every NTEE1 industry in a dataframe called "NTEE1zip" which I made in USEast15 (Part 1). (This dataframe actually also has H for every group, so I didn't need to recreate H--but it is nice to see that my new H matches up exactly with the H I had before.)
```{r}
load("/home/samutavi/Documents/Coe College/Spellman 2018/RData/NTEE1zip.Rdata")
Group$G <- NTEE1zip$G
coagg <- merge(coagg, Group, all = T)
#Grabbing the correct X from this dataframe as well.
Group$X <- NTEE1zip$X
```
Now I need to create two columns in the coagg dataframe. One is $\hat\gamma_jw_j^2(1-H_j)$, which I will aggregate by group and call J, and the other is $w_j^2$ which I will aggregate by group and call W.
```{r}
coagg$addtoJ <- (coagg$gammahat)*(coagg$wsubj^2)*(1-coagg$Hsubj)
J <- aggregate(coagg$addtoJ[!is.nan(coagg$addtoJ)],
               list(coagg$Group[!is.nan(coagg$addtoJ)]),
               sum)
colnames(J) <- c("Group", "J")
Group <- merge(Group, J, all = T)
```
Now for W:
```{r}
coagg$addtoW <- coagg$wsubj^2
W <- aggregate(coagg$addtoW,
               list(coagg$Group),
               sum)
colnames(W) <- c("Group", "W")
Group <- merge(Group, W, all = T)
```
Now I have all the variables I need in Group to calculate "GammaCoagg".
```{r}
rm(H)
rm(W)
rm(J)
Group$GammaCoagg <- ((Group$G/(1-Group$X))-Group$H-Group$J)/(1-Group$W)
```
I am very interested in comparing this gamma to the agglomeration metric I got for the NTEE1 industries, so I'm going to add that gamma to this dataframe. For a sense of how big each industry is, I'm also going to include the frequency of the NTEE1 category.
```{r}
Group$GammaAgglom <- NTEE1zip$gamma
Group$freq <- NTEE1zip$freq
```
And to finish up, I will plot a histogram of GammaCoagg, to get an idea of the distribution.
```{r}
library(ggplot2)
gammacoagg <- ggplot(data = Group, aes(x=GammaCoagg)) + 
  geom_histogram(binwidth = .025, fill="black", col="gray") +
  xlim(-.3, .2)
#Takes out gridlines, background, and creates neater appearance
gammacoagg + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"), text = element_text(size=20), plot.title = element_text(hjust = 0.5)) + labs(title = "NP gammas of coagglomeration", x = "Gamma Coagg", y = "Number of groups")
ggsave("gammacoagg.jpg", width = 16, height = 9)

```

I'm interested in the correlation between the NTEE1 agglomeration gamma and the Group coagglomeration gammas. 

```{r}
plot(Group$GammaCoagg, Group$GammaAgglom)

finite <- subset.data.frame(Group, Group != "Z")
cor(finite$GammaCoagg, finite$GammaAgglom)
```

I want to save the Group data frame as an RData file for future use.

```{r}
save(Group, file = "/home/samutavi/Documents/Coe College/Spellman 2018/USEast2015/Output/EGCoagg.Rdata")
```

