---
title: "EG Metric Simulations"
output:
  pdf_document: default
  html_notebook: default
  toc: true
---
#Purpose
In this document, I want to replicate the EG metric for agglomeration for a test dataset to see if the metric is working as I expect. I will follow the structure of my previous document, EG Metric Replication, Part 3, which replicates the metric for every industy and sector in Cedar Rapids.
```{r}
load("/home/samutavi/Documents/Coe College/Spellman 2018/RData/EGSimulation.Rdata")
EGSimulation
```

#Method
I have a variable called "size" and I will use the variable "area" for geographic units. There are nine areas, numbered 1 to 9. So far, I have made 6 industries in three "sizes"--either 1, 5, or 10. 

$i$ will be given by "area".

$z_k$ is each NP establishment's share of total "Industry" revenue (that is, the one-letter industry designation)

$x_i$ is $i$'s share of "sector" revenue

With these three variables, we would find the following:

$s_i$ would be constructed from $z_k$, using only establishments inside $i$, for each one-letter industry

$G$ would be constructed from $s_i$ and $x_i$, for each one-letter industry

$H$ comes from a Herfindahl of $z_k$, for each one-letter industry

These variables would give $\gamma$, which is the EG measure of agglomeration. I want a gamma for every one-letter industry.

#Sector and Industries
This simulation has six industries, named A, B, C, D, E, and F. A, B, and C belong to sector ABC and D, E, and F belong to sector DEF. In sector ABC, every industry is evenly dispersed, with one firm in each area. In sector DEF, every industry is completely clustered in a single area. I expect gamma to be 0 in every industry in sector ABC, and 1 for every industry in sector DEF. 

#Creating Necessary Variables

##Creating $z_k$
The first step is to create a variable called "zsubk" which is every nonprofit's share of total size in its own industry. First, I need a data set of "size" subtotals by industry.
```{r}
industries <- aggregate(EGSimulation$Size, 
          list(EGSimulation$Industry),
          sum)
colnames(industries) <- c("Industry", "r")
industries
```
Now I need to divide each nonprofit's total revenue by the appropriate number from the dataset above, depending on the industry industry. The easiest way to do this is probably to create a new column in EGSimulation that has the relevant subtotal for each nonprofit. 

```{r}
EGSimulation$subtotals <- industries$r[ match(EGSimulation$Industry, industries$Industry) ]

```

Next, I will create a vector "zsubk" which is each establishment's total revenue divided by the sum given above.
```{r}
EGSimulation$zsubk <- EGSimulation$Size/EGSimulation$subtotals
EGSimulation$zsubk
sum(EGSimulation$zsubk) #Checking that the individual shares add to 6.
```
 
This gives $z_k$. This is correct so far, since each nonprofit in the simulation has the same size relative to its own industry.

##Creating $x_i$
Next, I want to find $x_i$ which is each area's share of total sector size. For this, I'll need to aggregate by area and "sector" to find subtotals for each one, and then I also need the totals for each sector. 
```{r}
areas <- aggregate(EGSimulation$Size,
                       list(EGSimulation$Area, EGSimulation$Sector),
                       sum)
colnames(areas) <- c("area", "sector", "subtotal")
areas

sectortotals <- aggregate(EGSimulation$Size,
                       list(EGSimulation$Sector),
                       sum)
colnames(sectortotals) <- c("sector", "sectortotal")
sectortotals
#Now to merge the two datasets.
areas <- merge(areas, sectortotals, all = TRUE)
#Then I get xsubi for every zip code by dividing.
areas$xsubi <- areas$subtotal/areas$sectortotal
#The sum of all the xsubis should be 2.
sum(areas$xsubi)
```

##Creating $s_i$
Now I have $z_k$ and $x_i$. Using $z_k$, I need to get $s_i$ for every area. This is defined as $s_i=\sum_k{z_k}{u_{ki}}$ where $u_{ki}$ is an indicator variable equal to 1 if establishment $k$ is in $i$ and equal to 0 if $k$ is not in $i$. I need a different $s_i$ for every industry, so basically I need to aggregate just the establishments in each area AND industry to find subtotals of the variable I've called "zsubk". 

```{r}
areas2 <- aggregate(EGSimulation$zsubk, 
                      list(EGSimulation$Area, EGSimulation$Industry),
                      sum)
colnames(areas2) <- c("area", "industry", "ssubi")
sum(areas2$ssubi)
sum(areas2$ssubi[areas2$industry == "A"]) #Checking that any given industry totals to 1.
```
```{r}
#Checking that there are no values of ssubi that are above 1.
length(areas2$ssubi)
length(areas2$ssubi[areas2$ssubi > 1])
sum(areas2$ssubi)
```

##Finding $G$ for Industry P
Now I add these "xsubi" values to the data frame "areas2" in a column called "xsubi". I use the merge function for this. However, it's tricky because at this stage I need to specify which sector each industry belongs to. So first, I will create a column called sector in the areas2 dataframe that gives the correct sector. Then hopefully they will merge correctly based on both zipcode and sector variables.
```{r}
areas2$sector <- EGSimulation$Sector[ match(areas2$industry, EGSimulation$Industry)]
#That worked! Now to merge correctly...

areas <- merge(areas, areas2, by=c("area", "sector"))

areas
```
With this dataset, I can find G. $G=\sum_i{(s_i-x_i)^2}$

```{r}
areas$geocon <- (areas$ssubi-areas$xsubi)^2
Gbyindustry <- aggregate(areas$geocon, 
              list(areas$industry),
              sum)
colnames(Gbyindustry) <- c("Industry", "G")
industries <- merge(industries, Gbyindustry, all = TRUE)
```
Now I have a vector of G values by industry, which is exactly what I want.

##Finding $H$ for Every Industry
Now I can use zsubk to find the Herfindahl index given by $H=\sum_k{z_k^2}$ for every industry.
```{r}
library(hhi)
?hhi
class(EGSimulation$zsubk)
H <- by(EGSimulation, list(EGSimulation$Industry), function(x) hhi(x, "zsubk"), simplify = FALSE)
#Now I need this as a dataframe.
H <- cbind(H)
H <- unlist(H)
industries <- cbind(industries, H)

```
##Finding $X$ for Every Industry
The last thing I need in order to find $\gamma$ for every industry is $\sum{x_i^2}$, which I will just call "X". Again, I can use "by" to apply my function to subsets of the dataframe.

```{r}
X <- by(areas$xsubi, list(areas$industry), function(x) sum(x^2), simplify = FALSE)
X <- cbind(X)
X <- unlist(X)
industries <- cbind(industries, X)

```

#Result
Now I have G, H, and X by industry in a dataframe called industries. I can use those three to come up with $\gamma$, using the EG definition of $\gamma$.

$$\gamma=\frac{G-(1-\sum{x_i^2})H}{(1-\sum{x_i^2})(1-H)}$$
that is,
$$\gamma=\frac{G-(1-X)H}{(1-X)(1-H)}$$
```{r}
attach(industries)
industries$gamma <- (industries$G-(1-industries$X)*industries$H)/((1-industries$X)*(1-industries$H))
industries$gamma
```
This is not quite what I expected, but it may help me troubleshoot my metric. Either my expectations were wrong or the calculations were wrong. Anyway, I will finish the calculations in the document just as I did for EG Metric Replication, Part 3.

```{r}
library(plyr)
np <- count(EGSimulation, "Industry")
names(np)[1] = "Industry"
industries <- merge(industries, np)
industries

```
```{r}
plot(industries$gamma, industries$freq)
```
